Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2021-09-24 mice_synthesizing/paper.Rmd
some models to eval added

- [x] Explain FCS in short.
- [ ] Demonstrate procedure with `where-matrix` and explain rationale.
- [ ] Demonstrate that this is a reasonable approach, based on a figure that shows the observed and synthetic relationships side-by-side (e.g. `wgt ~ age + gen`).
- [ ] Observed values can be regarded as starting values for the imputation model. Since the observed data is used for creating the imputation models, no iterations are required. That is, the model is fixed, and not dependent on the imputed values.

@@

>>>>

- [x] Explain FCS in short.
- [x] Demonstrate procedure with `where-matrix` and explain rationale.
- [ ] Demonstrate that this is a reasonable approach, based on a figure that shows the observed and synthetic relationships side-by-side (e.g. `wgt ~ age + gen`).
- [ ] Observed values can be regarded as starting values for the imputation model. Since the observed data is used for creating the imputation models, no iterations are required. That is, the model is fixed, and not dependent on the imputed values.

@@

# psych::describe
# correlation matrix
# wgt ~ age + bmi | hgt ~ age + wgt | gen ~ age +

```{r}
library(mice)
library(dplyr)
library(magrittr)
meth <- make.method(boys)
meth["bmi"] <- "~ I(wgt / (hgt / 100)^2)"
pred <- make.predictorMatrix(boys)
pred[c("hgt", "wgt"), "bmi"] <- 0
imp <-mice(boys, 
           meth = meth, 
           pred = pred, 
           print = FALSE)
with(imp, lm(wgt ~ age + bmi))%>% pool() %>% summary()
with(imp, lm(bmi ~ I((wgt / (hgt/100)^2))))%>% pool() %>% summary()
library(MASS)
with(imp, polr(gen ~ age + bmi, Hess = TRUE)) %>% pool() %>% summary()
```

# log reg prediction of rows
